---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# analytics

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

## Overview

This package provides a dashboard for the [**shiny**](https://shiny.rstudio.com) applications that provides graphical user interfaces for the [tesselle](https://www.tesselle.org) packages.

## Installation

You can install the latest version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/analytics")
```

## Usage

```{r shiny, eval=FALSE}
## Load the package
library(analytics)

## Run the dashboard
run_dashboard()
```

## Contributing

Please note that the **kinesis** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.
